Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md
minor eds

Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer2016] and could explain movement between islands. Conspecific
competition for resources driven by reduced foraging opportunities can decrease
reproductive success of adult females [@Schaefer2016].Forage scarcity has been
proposed as a potential reason for caribou moving between arctic islands on the
sea-ice in winter [@Miller1977]. Caribou were introduced to Fogo Island (n = 26
animals between 1964–67) and Change Island (n = 5 animals in 1964) from
Newfoundland as part of a series of translocations and introductions throughout
the province (Bergerud & Mercer 1989). It is unknown when caribou began
colonizing nearby islands, but given that some are small, over-grazing by newly
arrived caribou may rapidly deplete forage [@Bergerud1990]. Although
unconfirmed, it is also possible that Fogo Island has experienced forage
depletion since the introduction of caribou in the 1960s. More likely, however,
is fine-scale competition for foraging resources that drives caribou to swim to
new islands.

>>>>

Forage limitation and over-grazing is a major concern for caribou populations
[@Schaefer2016] and could explain movement between islands. Conspecific
competition for resources driven by reduced foraging opportunities can decrease
reproductive success of adult females [@Schaefer2016]. Forage scarcity has been
proposed as a potential reason for caribou moving between arctic islands on the
sea-ice in winter [@Miller1977]. Caribou were introduced to Fogo Island (n = 26
animals between 1964–67) and Change Island (n = 5 animals in 1964) from
Newfoundland as part of a series of translocations and introductions throughout
the province (Bergerud & Mercer 1989). It is unknown when caribou began
colonizing nearby islands, but given that some are small, over-grazing by newly
arrived caribou may rapidly deplete forage on an annual cycle [@Bergerud1990]. Although
unconfirmed, it is also possible that Fogo Island has experienced forage
depletion since the introduction of caribou in the 1960s. More likely, however,
is fine-scale competition for foraging resources that drives caribou to swim to
new islands.
